Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/introduction.tex
Added an asedit command.

\xhdr{Additional findings.}
We investigate the ``first-mover advantage" phenomenon in more detail. Being first in the market gives free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage"). We run additional experiments so as to isolate and compare these two effects. We find that either effects alone leads to a significant advantage under competition. The data advantage is larger than reputation advantage when the incumbent commits to a more advanced bandit algorithm.

>>>>

\xhdr{Additional findings.}
We investigate the ``first-mover advantage" phenomenon in more detail. Being first in the market gives free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage"). We run additional experiments so as to isolate and compare these two effects. \asedit{We find that either effects alone leads to a significant advantage under competition. The data advantage is larger than reputation advantage when the incumbent commits to a more advanced bandit algorithm.}
